---
title: "Stat 479 Final Project"
author: "Evan O'Keefe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
```

```{r}
geo_url = "https://data.cityofnewyork.us/api/geospatial/d3c5-ddgc?method=export&format=GeoJSON"

city_sf <- read_sf(geo_url, as_tibble = TRUE) %>% 
  st_transform(2263) %>% 
  select(objectid, zone, borough)

manhattan_sf <- city_sf %>% 
  filter(borough == "Manhattan")

zones <- c("Battery Park City",
           "Central Harlem North",
           "East Harlem North",
           "Hudson Sq",
           "Inwood",
           "Inwood Hill Park",
           "Marble Hill",
           "Meatpacking/West Village West",
           "Union Sq",
           "West Village")

p <- manhattan_sf %>% 
  filter(zone %in% zones) %>% 
  ggplot() +
    geom_sf(data = manhattan_sf, fill = "white") +
    geom_sf(aes(fill = zone)) +
    theme_void() +
    theme(legend.position = "None")

ggsave('hood_map.png', p, bg='transparent')
```


```{r}
all_data <- read_csv("data/pu_data.csv")

df <- all_data %>% 
  group_by(objectid) %>% 
  summarise_at(vars(trip_distance:count), sum)

rides_sf <- manhattan_sf %>% 
  merge(df)

ggplot(rides_sf) +
  geom_sf(data = manhattan_sf, fill = "white") +
  geom_sf(aes(fill = tip_amount / total_amount * 100)) +
  scale_fill_distiller(name = "", direction = 1, palette='Greens') +
  theme_void()
```

```{r}
library(gganimate)
library(transformr)

rides <- read_csv("data/pu_data.csv") %>%
  mutate(date = paste(year, month, sep = "-")) %>% 
  group_by(objectid, date) %>% 
  summarise_at(vars(trip_distance:count), sum)

rides_sf <- manhattan_sf %>% 
  merge(rides)

anim <- ggplot(rides_sf, aes(group=seq_along(date))) +
  geom_sf(data = manhattan_sf, fill = "red") +
  geom_sf(aes(fill = avg_tips)) +
  scale_fill_distiller(
    name='Percentage',
    breaks = c(0, 5, 10, 15, 20, 25),
    direction = 1,
    palette='Greens',
    guide = guide_colorbar(frame.colour = "black", barwidth = 2, barheight = 30, nbins = 6)
    ) +
  theme_void(base_size = 30) +
  theme(plot.title = element_text(face = "bold")) +
  labs(
    title = 'Manhattan Yellow Taxi Average Tips By Month',
    subtitle = '{paste(month(closest_state), year(closest_state), sep="/")}'
    ) +
  transition_states(date) 

animate(p, height = 1200, width = 1200, fps= 5, nframes=120, renderer=gifski_renderer())
anim_save("avgtips.gif")
```
rides_sf%>%
  group_by(zone)%>%
  summarize(first(objectid),tips = mean(avg_tips))%>%
  arrange(desc(tips))

zones = c(13,125,249,158,234,153,128,42,74,127)

ezplot = rides_sf%>%
  filter(objectid %in% zones)

p = ggplot(ezplot, aes(x = date, y = avg_tips))+
  geom_smooth(aes(color = zone), se = F)+
  theme_bw() +
  theme(plot.title = element_text(face = "bold")) +
  labs(
    title = 'Average Tips By Month & Neighborhood',
    x = 'Date of Measure',
    y = 'Average Tips'
    )
ggsave("manhattanTrends.png", p)
```

```{r}
library(ggpubr)
library(rstatix)
library(eeptools)

rides_aov = rides_sf%>%
  st_drop_geometry()%>%
  select(zone, date, avg_tips)%>%
  group_by(zone,date)%>%
  summarize(avg_tips = mean(avg_tips))%>%
  ungroup()

res.aov <- rstatix::anova_test(data = rides_aov, dv = avg_tips, wid = zone, within = date)
get_anova_table(res.aov)

```

```{r, fig.height=1200, fig.width=1200}

brooklyn_sf <- city_sf %>% 
  filter(borough == "Brooklyn")
all_data <- read_csv("data/all_data.csv")

df <- all_data %>% 
  group_by(objectid) %>% 
  summarise_at(vars(trip_distance:count), sum)

rides_sf <- brooklyn_sf %>% 
  merge(df)

p <- ggplot(rides_sf) +
  geom_sf(data = manhattan_sf, fill = "white") +
  geom_sf(aes(fill = total_amount * 100)) +
  scale_fill_distiller(name = "", direction = 1, palette='Greens') +
  theme_void() +
    labs(title = 'Manhattan Yellow Taxi Revenue', subtitle = "June")

ggsave("test.png", p)
```

```{r}
library(gganimate)
library(lubridate)
library(transformr)
library(gifski)

rides <- read_csv("data/pu_data.csv") %>% 
  mutate(date = my(paste(month,year,sep="/")))%>%
  group_by(objectid, date) %>% 
  summarise_at(vars(trip_distance:count), sum)

rides_sf_b <- brooklyn_sf %>% 
  merge(rides)%>%
  mutate(avg_tips = (tip_amount/total_amount)*100)

p <- ggplot(rides_sf_b, aes(group=seq_along(date))) +
  geom_sf(data = brooklyn_sf, fill = "red") +
  geom_sf(aes(fill = avg_tips)) +
  scale_fill_distiller(
    name='Percentage',
    breaks = c(0, 5, 10, 15, 20, 25),
    direction = 1,
    palette='Greens',
    guide = guide_colorbar(frame.colour = "black", barwidth = 2, barheight = 30, nbins = 6)
    ) +
  theme_void(base_size = 30) +
  theme(plot.title = element_text(face = "bold")) +
  labs(
    title = 'Brooklyn Yellow Taxi Average Tips By Month',
    subtitle = '{paste(month(closest_state), year(closest_state), sep="/")}'
    ) +
  transition_states(date) 

animate(p, height = 1200, width = 1200, fps= 5, nframes=120, renderer=gifski_renderer())
anim_save("avgtips_brooklyn.gif")
```

```{r}
library(ggpubr)
library(rstatix)
library(eeptools)

rides_aov_b = rides_sf_b%>%
  st_drop_geometry()%>%
  select(zone, date, avg_tips)%>%
  group_by(zone,date)%>%
  summarize(avg_tips = mean(avg_tips))%>%
  ungroup()

res.aov.b <- anova_test(data = rides_aov_b, dv = avg_tips, wid = zone, within = date)
get_anova_table(res.aov.b)

```

```{r}
rides_sf_b%>%
  st_drop_geometry()%>%
  group_by(zone)%>%
  summarize(first(objectid),tips = mean(avg_tips))%>%
  arrange(tips)

zones = c(52,40,255,33,66,71,222,35,72,77)

ezplot = rides_sf_b%>%
  filter(objectid %in% zones)

p = ggplot(ezplot, aes(x = date, y = avg_tips))+
  geom_smooth(aes(color = zone), se = F)+
  theme_bw() +
  theme(plot.title = element_text(face = "bold")) +
  labs(
    title = 'Average Tips By Month & Neighborhood',
    x = 'Date of Measure',
    y = 'Average Tips'
    )
ggsave("brooklyn_trends.png", p)
```
